\textsc{RILS}-\textsc{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-27 paper_resources/doc/paper.tex

SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}. It brings researchers an easy handled environment to evaluate, compare, and analyze their methods. Among all benchmark sets, we involve two real-world inspired ground-truth benchmark sets that represent types of regression problems, into our computational evaluation: 
\begin{itemize}
	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that describes   various natural laws.  
	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.  Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to the results reported in~\cite{la2021contemporary}.

>>>>

SRBench is an open-source benchmarking project which merge a large set of diverse benchmark datasets, contemporary SR methods as well as ML methods around a shared model evaluation and an environment for analysis, see~\cite{la2021contemporary}. It brings researchers an easy handled environment to evaluate, compare, and analyze their methods.  We involve two real-world inspired ground-truth benchmark sets that represent types of regression problems, into our computational evaluation: 
\begin{itemize}
	\item \textsc{Feynman} benchmark set, inspired from physics and formulas/models that describes   various natural laws.  
	It consists of $10^5$  samples, each described in~\cite{udrescu2020ai}. Some exact models (equations) of problem instances from this benchmark are shown in Table~\ref{tab:Feynamn-Eq}.  Among them, 116 regression problem instances are chosen in the experimental evaluation, with accordance to the results reported in~\cite{la2021contemporary}.
